---
title: "Exploration 4:  Estimators"
author: "Mannie Chomsin"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r, message = FALSE, warning = FALSE}
library("ggplot2")

# This randomly generates 25 random numbers between zero and one
one_sample <- runif(25)

# Note that the population variance formula does not have "n - 1"
bad_var <- function(x){
  N <- length(x)
  sigma_squared <- sum( (x - mean(x))^2 ) / N
  sigma_squared #return this number
}

# Note that the sample variance formula does have "n - 1"
good_var <- function(x){
  n <- length(x)
  s_squared <- sum( (x - mean(x))^2 ) / (n-1)
  s_squared #return this number 
}
```

## Example

Here we will run a simulation to empirically show that the *population mean*
$$\mu = \displaystyle\frac{1}{N} \sum_{i = 1}^{N} x_{i}$$
is **unbiased** when applied to samples over the $U(0,1)$ uniform distribution (whose true population mean is $\mu = \displaystyle\frac{1}{2}$).

```{r, eval = TRUE}
true_mean <- 1/2

simulation <- replicate(10000, mean( runif(25) )) #generates 25 random numbers btw 0-1 then means them, repeat 1000 times (mean of means)
df <- data.frame(simulation)

ggplot(df, aes(x = simulation)) +
  geom_density(color = "blue") + 
  geom_vline(xintercept = true_mean, color = "red") +
  labs(title = "Sample Distribution for the Sample Mean",
       subtitle = "Blue: sample distribution, Red: statistic of interest",
       caption = "Math 32")
```

Since the sample distribution empirically does seem to line up with the population mean, we say that the sample mean $\bar{x}$ is *unbiased*.

---

Repeat the simulation above, but with the an $Exp(1/32)$ distribution and the following estimators:

1.  sample median `median()`
```{r, eval = TRUE}
true_median <- log(2)*32 #median of continuous exponential distribution ln(2) divided by rate

simulation <- replicate(10000, median( rexp(25,1/32) )) #rexp is exponential distribution 
df <- data.frame(simulation)

ggplot(df, aes(x = simulation)) +
  geom_density(color = "blue") + 
  geom_vline(xintercept = true_median, color = "red") +
  labs(title = "Sample Distribution for the Sample Median",
       subtitle = "Blue: sample distribution, Red: statistic of interest",
       caption = "Math 32")
```

This is probably unbiased of and estimator because the median is close to the middle/peak of the bell curve


2.  population variance `bad_var()`
```{r, eval = TRUE}
true_var <- 32^2 #variance of exp distribution is 1/(lamda^2)

simulation <- replicate(10000, bad_var( rexp(25,1/32) )) 
df <- data.frame(simulation)

ggplot(df, aes(x = simulation)) +
  geom_density(color = "blue") + 
  geom_vline(xintercept = true_var, color = "red") +
  labs(title = "Sample Distribution for the Population Variance",
       subtitle = "Blue: sample distribution, Red: statistic of interest",
       caption = "Math 32")
```

This is a biased estimator because the true variance and the peak of the distribution are kind of distant, theres an over estimate. 


3.  sample variance `good_var()`
```{r, eval = TRUE}
true_var <- 32^2 #variance of exp distribution is 1/(lamda^2)

good_var <- function(x){
  n <- length(x)
  s_squared <- sum( (x - mean(x))^2 ) / (n-1)
  s_squared #return this number 
}

simulation <- replicate(10000, good_var( rexp(25,1/32) )) 
df <- data.frame(simulation)

ggplot(df, aes(x = simulation)) +
  geom_density(color = "blue") + 
  geom_vline(xintercept = true_var, color = "red") +
  labs(title = "Sample Distribution for the Sample Variance",
       subtitle = "Blue: sample distribution, Red: statistic of interest",
       caption = "Math 32")
```

Unbiased estimator because the peak of the curve/middle of the area of the curve and the red prediction line are closer.


4.  the sample standard deviation from `good_var()`
```{r, eval = TRUE}
true_sd <- 32 #standard deviation for exp is mean which is 1/lambda

simulation <- replicate(10000, sqrt(  good_var( rexp(25,1/32) )  )) 
df <- data.frame(simulation)

ggplot(df, aes(x = simulation)) +
  geom_density(color = "blue") + 
  geom_vline(xintercept = true_sd, color = "red") +
  labs(title = "Sample Distribution for the Sample SD",
       subtitle = "Blue: sample distribution, Red: statistic of interest",
       caption = "Math 32")
```

Unbiased estimator because the peak of the curve and the red prediction are pretty close


---

After each simulation, make an educated guess as to whether each estimator is biased or unbiased.

---

Verify that you have 5 graphs in total and replace "Math 32" with your full name in all of the graphs.

Finally, `knit` your work as either an HTML or PDF document, and upload that document back into the CatCourses assignment.
