---
title: "Math 32:  Exploration 3"
author: "Mannie Chomsin"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
        theme: cerulean
---

In this `exploration`, you are asked to

* generate random numbers from continuous distributions
* observe the visualizations of those number sets

1. First,
    a. Type your name into the author field in the YAML parameters above
    b. Also save this file while replacing "template" with your full name (be sure to keep the *.rmd file format).

```{r, message = FALSE, warning = FALSE}
library("ggplot2")
```

# Uniform Distribution

2. Demonstrate your understanding about the example code block below by adding at least 5 comments in the code block in your own words.

```{r}
N <- 1000   #assigns variable N value 1000
a <- 1      #assigns variable a value 1
b <- 32     #assigns variable b value 32
data <- runif(N, a, b) #creates iteratible of 1000 elements randomly between 1 and 32
df <- data.frame(data) #makes dataframe with iteratible data as column and calls it df

ggplot(df, aes(y = data)) +   #Creates boxplot with data from df. 
  coord_flip() +
  geom_boxplot() +
  labs(title = paste0("Uniform Distribution U(", a, ",", b, ")"), #label it "Uniform Distribution"
       subtitle = "boxplot",
       caption = "Math 32") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  ylim(0,50) #Limit y axis to between 0 and 50

ggplot(df, aes(x = data)) +   #Creates graph of density by number
  geom_density(kernel = "gaussian") +
  labs(title = paste0("Uniform Distribution U(", a, ",", b, ")"),
       subtitle = "density plot",
       caption = "Math 32") +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlim(0,50)  #Limit x axis to between 0 and 50
```

3. Repeat step 2 in a new code block, but with different values of $a$ and $b$ in $0 < a < b < 50$
```{r}
N <- 1000   #assigns variable N value 1000
a <- 25      #assigns variable a value 30
b <- 49      #assigns variable b value 54
data <- runif(N, a, b) #creates iteratible of 1000 elements randomly between 1 and 32
df <- data.frame(data) #makes dataframe with iteratible data as column and calls it df

ggplot(df, aes(y = data)) +   #Creates boxplot with data from df. 
  coord_flip() +
  geom_boxplot() +
  labs(title = paste0("Uniform Distribution U(", a, ",", b, ")"), #label it "Uniform Distribution"
       subtitle = "boxplot",
       caption = "Math 32") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  ylim(0,50) #Limit y axis to between 0 and 50

ggplot(df, aes(x = data)) +   #Creates graph of density by number
  geom_density(kernel = "gaussian") +
  labs(title = paste0("Uniform Distribution U(", a, ",", b, ")"),
       subtitle = "density plot",
       caption = "Math 32") +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlim(0,50)  #Limit x axis to between 0 and 50
```
4. Make at least two observations about the results (the graphs) in an unordered list.

*Changine the range the random numbers are sampled from moves the mean and range of the function
*The density can be larger than the biggest and lowest numbers

# Normal Distribution

5. Make adjustments to the code below to repeat what was done above with the uniform distribution, but this time looking at the normal distribution (hint: use the `rnorm` command).

```{r}
N <- 1000
a <- 1
b <- 32
data <- rnorm(N, a, b)
df <- data.frame(data)

ggplot(df, aes(y = data)) +
  coord_flip() +
  geom_boxplot() +
  labs(title = paste0("Normal Distribution N(", a, ",", b, ")"),
       subtitle = "boxplot",
       caption = "Math 32") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  ylim(0,50)

ggplot(df, aes(x = data)) +
  geom_density() + 
  labs(title = paste0("Normal Distribution N(", a, ",", b, ")"),
       subtitle = "density plot",
       caption = "Math 32") +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlim(0,50)
```

6. Repeat step 5 in a new code block, but with different values of $a$ and $b$ in $0 < a < b < 50$
```{r}
N <- 1000
a <- 20
b <- 40
data <- rnorm(N, a, b)
df <- data.frame(data)

ggplot(df, aes(y = data)) +
  coord_flip() +
  geom_boxplot() +
  labs(title = paste0("Normal Distribution N(", a, ",", b, ")"),
       subtitle = "boxplot",
       caption = "Math 32") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  ylim(0,50)

ggplot(df, aes(x = data)) +
  geom_density() + 
  labs(title = paste0("Normal Distribution N(", a, ",", b, ")"),
       subtitle = "density plot",
       caption = "Math 32") +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlim(0,50)
```
7. Make at least two observations about the results (the graphs) in an unordered list.

* numbers no longer contained within 0 to 50
* density smaller
# Exponential Distribution

8. Make adjustments to the code below to repeat what was done above with the uniform distribution, but this time looking at the exponential distribution with $\lambda = \frac{1}{\mu}$ (hint: use the `rexp` command).

```{r}
N <- 1000
mu <- 32
data <- rexp(N,mu)
df <- data.frame(data)

ggplot(df, aes(y = data)) +
  coord_flip() +
  geom_boxplot() +
  labs(title = paste0("Exponential Distribution E(1/", mu, ")"),
       subtitle = "boxplot",
       caption = "Math 32") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  ylim(-.1,.3)

ggplot(df, aes(x = data)) +
  geom_density() +
  labs(title = paste0("Exponential Distribution E(1/", mu, ")"),
       subtitle = "density plot",
       caption = "Math 32") +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlim(-.1,.3)
```

9. Repeat step 8 in a new code block, but with different a value of $\mu$ in $0 < \mu < 50$
```{r}
N <- 1000
mu <- 40
data <- rexp(N,mu)
df <- data.frame(data)

ggplot(df, aes(y = data)) +
  coord_flip() +
  geom_boxplot() +
  labs(title = paste0("Exponential Distribution E(1/", mu, ")"),
       subtitle = "boxplot",
       caption = "Math 32") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  ylim(-.1,.3)

ggplot(df, aes(x = data)) +
  geom_density() +
  labs(title = paste0("Exponential Distribution E(1/", mu, ")"),
       subtitle = "density plot",
       caption = "Math 32") +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  xlim(-.1,.3)
```
10. Make at least two observations about the results (the graphs) in an unordered list.

* increasing mu makes the max data values smaller 
* increasing mu makes the max density larger

11.  Verify that you have 12 graphs in total (6 boxplots and 6 density plots), and replace "Math 32" with your full name in all of the graphs.

12. Finally, `knit` your work as either an HTML or PDF document, and upload that document back into the CatCourses assignment.