---
title: "Exploration 1"
author: "Wyssanie Chomsin"
date: "1/26/2020"
output: 
  html_document:
        theme: cerulean
---

# Math 32
## Exploration 1

In this `exploration`, you are asked to

* simulate rolling two or three dice
* graph the results as histograms

1. First,
    a. Type your name into the author field in the YAML parameters above
    b. Also save this file while replacing "template" with your full name (be sure to keep the *.rmd file format).

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
```

```{r}
N  <- 10000
X1 <- sample(1:6, N, replace = TRUE) #Assigns to variable X1 a vector of length N containing N random integers between 1:6, in this case 10000 elements, replace alows repeated outcomes, in otherwords a disjoint probabilty of getting each number 1 to 6
X2 <- sample(1:6, N, replace = TRUE) #X2 Is assigned to a different vector of length N containing another series of N random integers between 1 and 6

sums <- X1 + X2 # adds the corresponding elements of vectors X1 and X2 by index and assignes the resulting vector to variable sums.

df <- data.frame(sums) #Creates a data.frame with one column named sums containing the vector sums and saves it to the varible df

#Use ggplot2 library of tidyverse to create and label a histogram of the distribution of the sums sample
ggplot(df, aes(x = sums)) +
  geom_histogram(binwidth = 1, color = "black", fill = "white") +
  labs(title = "Two Dice",
       subtitle = "Simulation of dice rolls",
       caption = "Math 32") +
  scale_x_continuous(name = "total", breaks = 2:12)
```

2. Demonstrate your understanding about the above example code block above by adding at least 5 comments in your own words.

3. Make at least two observations about the results (the graph) in an unordered list.
    * Bell Shapped curve
    * Most common result is 7 (one more than the sides of dice)

4. Now let us try a more complicated setting.  In a new code block,
    * simulate rolling *three* dice at a time
    * run the simulation for at least 20,000 iterations
    * change the $x$-axis tick marks since the sample space is now $\{3, 4, ..., 18\}$
    * change the color that is *inside* of the rectangles
    * replace "Math 32" with your name in the caption

```{r}
N  <- 20000
X1 <- sample(1:6, N, replace = TRUE) #Assigns to variable X1 a vector of length N containing N random integers between 1:6, in this case 10000 elements, replace alows repeated outcomes, in otherwords a disjoint probabilty of getting each number 1 to 6
X2 <- sample(1:6, N, replace = TRUE) #X2 Is assigned to a different vector of length N containing another series of N random integers between 1 and 6
X3 <- sample(1:6, N, replace = TRUE)

sums <- X1 + X2 + X3 # adds the corresponding elements of vectors X1 and X2 by index and assignes the resulting vector to variable sums.

df <- data.frame(sums) #Creates a data.frame with one column named sums containing the vector sums and saves it to the varible df

#Use ggplot2 library of tidyverse to create and label a histogram of the distribution of the sums sample
ggplot(df, aes(x = sums)) +
  geom_histogram(binwidth = 1, color = "black", fill = "pink") +
  labs(title = "Three Dice",
       subtitle = "Simulation of dice rolls",
       caption = "Wyssanie (Mannie) Chomsin") +
  scale_x_continuous(name = "total", breaks = 3:18)
```
    
5. Make at least two observations about your new results (the graph) in an unordered list.
    * Still a bell curve
    * Max count increases
6. Finally, `knit` your work as either an HTML or PDF document, and upload that document back into the CatCourses assignment.