---
title: "Cumulative Binomial Distribution"
author: "Derek Sollberger"
date: "2/7/2020"
output: html_document
---

There are 32 parking spaces in a row in a UC Merced parking lot.  Suppose that each parking space tends to be occupied about 81 percent of the time.

```{r, message = FALSE, warning = FALSE}
library("ggplot2")
```

```{r}
n <- 32
p <- 0.19 #open, so 1-p = 0.81 for an occupied parking space
```

1. What is the probability that exactly 4 of the parking spaces are open?

```{r}
dbinom(4, n, p)
```

2. What is the probability that at most 3 of the parking spaces are open?

```{r}
sum( dbinom(0:3, n, p) )
```

3. What is the probability that more than 5 of the parking spaces are open?

```{r}
sum( dbinom(6:32, n, p) )
```

4. What is the probability that at least one of the parking spaces are open?

```{r}
1 - dbinom(0, n, p)
```


# Probability Mass Function (PMF)

```{r}
probs <- dbinom(0:n, n, p)
df <- data.frame(probs)

ggplot(df, aes(x = 0:n, y = probs)) +
  geom_bar(stat = "identity", fill = "blue") +
  theme_minimal() +
  labs(title = "Binomial Distribution PMF",
       subtitle = "p = 0.19",
       caption = "Math 32",
       x = "open parking spaces",
       y = "probability")
```


# Cumulative Mass Function (CMF)

```{r}
probs <- pbinom(0:n, n, p) #note the change here compared to previous example
df <- data.frame(probs)

ggplot(df, aes(x = 0:n, y = probs)) +
  geom_bar(stat = "identity", fill = "blue") +
  theme_minimal() +
  labs(title = "Binomial Distribution CMF",
       subtitle = "p = 0.19",
       caption = "Math 32",
       x = "open parking spaces",
       y = "probability")
```